%----------------------------------------------------------------------------
\chapter{Summary}\label{Ch7}
%----------------------------------------------------------------------------
Here I will summarize my impressions while working on this project.
%----------------------------------------------------------------------------
\section{Azure Serverless}
%----------------------------------------------------------------------------
Overall I had a pleasant experience with Microsoft Azure. One doesn't have to know everything to start. Azure is most of the time well documented. I worked with services that got published recently e.g.\ Communication Services for email sending or Partial Document Update for CosmosDB. Most of the time I could use these by only reading the official documentation. On the rare occasion I needed a more specific solution, there were developers who already faced the same issue and came to some solution so I could figure out the missing parts by myself. So the usage of the software was for the most part straightforward and there is a fairly reliable community.

One aspect what developers often complain of is the difficulty of debugging the server side. Granted, the error messages were some of the time non-existent. Occasionally waiting a little bit longer solved the problem and the function worked afterwards. When it didn't help, testing out the service locally and following the small leads I got did, the issues turned out to be discoverable and solvable. Later on when I collected a bit of experience I could guess what caused the bug. Note, mine was only a small example, in a huge system it's probably not so easy and not a good idea to rely on assumptions.
%----------------------------------------------------------------------------
\section{Microservices}
%----------------------------------------------------------------------------
Another thing I became a big fan of are microservices. At first it took some time to figure out their usage but then it turned out to be a handy tool. I did not get lost in the code base which is a big plus especially in case of a big project. Testing and modifying the functions was straightforward, it wasn't a concern from which part of the API an error comes from, because there were distinct collections of files that were not dependent on each other.
Additional benefit of this is, that each microservice can have its own configuration, I didn't get lost among the installed packages which aren't even used by that function of the service.

The price for this convenience is that every microservice should be configured and published on its own. In my experience they save a lot more time than it takes to set up each of them, what went reasonably fast with Azure.
