%----------------------------------------------------------------------------
\chapter{Challenges and possible extensions}\label{Ch5}
%----------------------------------------------------------------------------

This is the application I could accomplish in the given time frame. Obviously it's not the best or most ideal solution to this problem. I will list a few things I would do differently next time or should be improved.

\begin{itemize}
	\item The user login would not be an acceptable solution in a real life environment. It is always a good idea to use an already existing and thoroughly tested service as Azure Active Directory. Instead of the hand written login, AD B2C should be introduced to this application.
	
	\item I should give more thought to the database structure and reshape it, if it turns out to be cumbersome to work with.
	
	\item Currently users can't delete anything from the database. Restaurants, orders and reviews should have a delete option.
\end{itemize}

Things that could be added to enhance the user experience:

\begin{itemize}
	\item At registration the restaurant users should get some feedback, that the registration was successful. Azure AD would solve this problem as well.
	
	\item Users could have a profile, which they could modify, maybe collect points or discounts if they use the app consistently.
	
	\item The feedback should be collected from the users after they actually went to the restaurant. This could be done via a timed email or if they would have a profile with the restaurants they can write a review for.
\end{itemize}